### 2018-08-08 paper/evaluation.tex
avail experiment

\paragraph*{PORs} We used a constant amount of 3 layers per routes (excluding the final, destination layer),
and a constant number of peers per layer $w_\layer$ of 16.
The latter heavily influences both the network overhead (the more, the bigger the headers), and the routes' availability (more peers means a better probability that at least one peer is online in a layer).
The default availability threshold $\theta$ is $10^-3$.

@@

>>>>

\paragraph*{\ac{SPOR}} We used a constant amount of 3 layers per routes (excluding the final, destination layer),
and a constant number of peers per layer $w_\layer$ of 16.
The latter heavily influences both the network overhead (the more, the bigger the headers), and the routes' availability (more peers means a better probability that at least one peer is online in a layer).
The default availability threshold $\theta$ is $10^-3$.

@@

\subsubsection{Traffic and availability} % (fold)
\label{ssub:traffic_and_availability}

\begin{figure}[t]
  \centering
  %\def\svgwidth{0.8\columnwidth}
  \includegraphics[width=0.9\columnwidth]{figures/avail.pdf}

  \caption{\label{fig:completion_vs_size}
  Availability of devices and number of messages waiting for reception.}
\end{figure}

% subsubsection traffic_and_availability (end)
